DSCI 445 Final Report

### 2025-12-13 Draft Folder/Intro.Rmd
Draft finalization

Plots for categorical variables

@@

>>>>

Plots for categorical variables (S.A.)

@@

```
**Description:** These plots show that subscription rates vary meaningfully across categorical variables, with certain jobs, higher education levels, specific contact methods (especially cellular), particular months, and prior campaign successes all associated with higher proportions of clients subscribing to a term deposit.

### 2025-12-13 Paper.Rmd
Draft finalization

---
title: "draft_group-6"
author: "Sandra Afrifa, Tigist Kefelew , Mussa Hassen, Waddah Alaahtani"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

>>>>

---
title: "DSCI 445 Final Report"
subtitle: "Machine Learning Models on A Bank Marketing Dataset"
author: "Sandra Afrifa, Tigist Kefelew , Mussa Hassen, Waddah Alaahtani"
output: pdf_document
---
